---
title: "Occupational Prestige Ratings"
date: "Last updated `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    code_folding: hide
---

The ratings by job title and job field are provided below. Fields are aggregated groupings of related job titles. See the [main page](https://occupational-prestige.github.io/opratings/index.html) for an overview of this project. More complete description is provided in the following manuscript:

[--- citation blinded for review ---]
<!-- 
> <font size="3">Hughes, B. T., Srivastava, S., Leszko, M., & Condon, D. M. (under review). Occupational Prestige: The Psychosocial Indicator of Socioeconomic Status. *Journal TBD*.</font>
-->

See [here](https://occupational-prestige.github.io/opratings/opcrosswalk.html) for a crosswalk of these ratings to older prestige ratings.

```{r, include = F}
knitr::opts_chunk$set(echo = T, message = F, warning = F)
```

```{r}
library(here) # for engaging with working environment
library(Hmisc) # for weighted means
library(DT) # for viewing data tables
library(tidyverse) # for data cleaning and manipulation
library(dataverse)
library(data.table)
```

```{r, results='asis'}
# load the data 
opratings = read.csv(here("data/opratings.csv"))
colnames(opratings) <- c("OPR Job Code", "OPR Job Title", "OPR Jobs 2016", "OPR Field Code", "OPR Field Title", "OPR Field 2016", "ONET SOC 2018 Code", "ONET SOC 2018 Title", "ONET SOC 2010 Code", "ONET SOC 2010 Title", "Census Code 1980", "Census Title 1980", "GSS Ratings 1989", "Census Code 2010", "Census Titles 2010", "GSS Ratings 2012")
                
opratings_db = opratings[,c("OPR Job Title", "OPR Jobs 2016", "OPR Field Title", "OPR Field 2016", "ONET SOC 2018 Code", "ONET SOC 2018 Title")] %>%
  DT::datatable( # put into interactive HTML table
    colnames = c("OPR Job Title", "OPR Job Rating", "Job Field Title", "Avg Field Rating", "ONET-SOC Code*", "ONET-SOC Title*"), #colnames
    options = list(
      lengthMenu = list(c(10, 50, -1), c('10', '50', 'All')),
        pageLength = 10
    ),
    filter = "top", # can filter
    rownames = F # don't need rownames
  )
opratings_db
```

\* Note that the ONET-SOC Codes and ONET-SOC Titles shown here are based on the values from 2018. These codes and labels are updated periodically. The raw data file also contains the codes and labels from 2010.
